---
title: "01_data_methods"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Packages}
if (!require("dplyr")) {
  install.packages("dplyr")
  require("dplyr")
}
if (!require("moments")) {
  install.packages("moments")
  require("moments")
}
if (!require("psych")) {
  install.packages("psych")
  require("psych")
}
if (!require("tidyverse")) {
  install.packages("tidyverse")
  require("tidyverse")
}
if (!require("ltm")) {
  install.packages("ltm")
  require("ltm")
}
if (!require("EFAtools")) {
  install.packages("EFAtools")
  require("EFAtools")
}
```

# dataset created from PLF repo script "01_RCT_data_clean_merging" in the "01_Created_datasets" folder
```{r Data}
plf_data <- read.csv("Raw_datasets/Merged_plf_data_2024_12_30.csv")
```

# Filter the dataset to non-missing BDI/BHS observations
```{r complete data prep}
# This is so that the design can be fully crossed instead of nested

# Remove month "-9" rows (created for lifetime C-SSRS info)
plf_data <- plf_data[plf_data$month != -9, ]

# Filter to complete data:
total_time_points <- 4

# Summarize at how many obs everyone has
time_points_summary <- plf_data %>%
  dplyr::group_by(id) %>%
  dplyr::summarize(
    BHS = sum(!is.na(bhs)),
    BDI = sum(!is.na(bdi))
  )
```

# Just BHS complete (4 waves; baseline + 1 wave)
```{r BHS complete}
# Filter to BHS == 4 observations
plf_data_bhs_complete_filter_1 <- plf_data %>%
  dplyr::filter(id %in% time_points_summary$id[time_points_summary$BHS > 3])

# Check how many people there are
bhs_unique_id_count_1 <- plf_data_bhs_complete_filter_1 %>%
  dplyr::summarize(total_unique_ids = n_distinct(id))

bhs_unique_id_count_1 # 89

# Filter to BHS >= 2 observations
plf_data_bhs_complete_filter_2 <- plf_data %>%
  dplyr::filter(id %in% time_points_summary$id[time_points_summary$BHS > 1])

# Remove people missing baseline (month 0)
plf_data_bhs_complete_filter_2 <- plf_data_bhs_complete_filter_2 %>%
  filter(!(month == 0 & is.na(bhs)))

# Check how many people there are
plf_data_bhs_complete_filter_2 %>%
  dplyr::summarize(total_unique_ids = n_distinct(id)) # N = 162

# But also make sure everyone *has* a month 0 row
ids_with_baseline <- plf_data_bhs_complete_filter_2 %>%
  filter(month == 0 & !is.na(bhs)) %>%
  pull(id) %>%
  unique()

# And only keep those 
plf_data_bhs_complete_filter_2 <- plf_data_bhs_complete_filter_2 %>%
  filter(id %in% ids_with_baseline)

# Check remaining unique IDs
plf_data_bhs_complete_filter_2 %>%
  summarise(total_unique_ids = n_distinct(id)) # N = 158
```

# Just BDI complete (4 waves; baseline + 1 wave)
```{r BDI complete}
# Filter to BDI == 4 observations
plf_data_bdi_complete_filter_1 <- plf_data %>%
  dplyr::filter(id %in% time_points_summary$id[time_points_summary$BDI > 3])

# Check how many people there are
bdi_unique_id_count_1 <- plf_data_bdi_complete_filter_1 %>%
  dplyr::summarize(total_unique_ids = n_distinct(id))

bdi_unique_id_count_1 # 87

# Filter to BDI +>2 observations
plf_data_bdi_complete_filter_2 <- plf_data %>%
  dplyr::filter(id %in% time_points_summary$id[time_points_summary$BDI > 1])

# Remove people missing baseline (month 0)
plf_data_bdi_complete_filter_2 <- plf_data_bdi_complete_filter_2 %>%
  filter(!(month == 0 & is.na(bdi)))

# Check how many people there are
plf_data_bdi_complete_filter_2 %>%
  dplyr::summarize(total_unique_ids = n_distinct(id)) # N = 162

# But also make sure everyone *has* a month 0 row
ids_with_baseline <- plf_data_bdi_complete_filter_2 %>%
  filter(month == 0 & !is.na(bdi)) %>%
  pull(id) %>%
  unique()

# And only keep those 
plf_data_bdi_complete_filter_2 <- plf_data_bdi_complete_filter_2 %>%
  filter(id %in% ids_with_baseline)

# Check remaining unique IDs
plf_data_bdi_complete_filter_2 %>%
  summarise(total_unique_ids = n_distinct(id)) # N = 157

# Is it the same sample in the BDI/BHS 2-wave data?
setequal(plf_data_bdi_complete_filter_2$id, plf_data_bhs_complete_filter_2$id) # no
setdiff(plf_data_bdi_complete_filter_2$id, plf_data_bhs_complete_filter_2$id) # 0
setdiff(plf_data_bhs_complete_filter_2$id, plf_data_bdi_complete_filter_2$id) # 1 
# For consistency across models, use the smaller sample 
```

# Complete BDI+BHS
```{r complete BDI and BHS}
# Filter to BHS and BDI-II == 4 observations
plf_data_complete_filter <- plf_data %>%
  dplyr::filter(id %in% time_points_summary$id[time_points_summary$BHS > 3 &
    time_points_summary$BDI > 3])

# Check how many people there are
unique_id_count <- plf_data_complete_filter %>%
  dplyr::summarize(total_unique_ids = n_distinct(id))

# Check how many people there are in each group
unique_id_by_arm_rec <- plf_data_complete_filter %>%
  dplyr::group_by(arm_rec) %>%
  dplyr::summarize(unique_ids = n_distinct(id))

# Confirm complete data
time_points_summary <- plf_data_complete_filter %>%
  group_by(id) %>%
  dplyr::summarize(
    BHS = sum(!is.na(bhs)),
    BDI = sum(!is.na(bdi))
  )

summary(time_points_summary$BHS)
summary(time_points_summary$BDI)

# Check for item-level missing data
plf_data_complete_filter %>%
  dplyr::select(contains("bdi")) %>%
  dplyr::summarize(across(everything(), list(
    mean = ~ mean(., na.rm = TRUE),
    sd = ~ sd(., na.rm = TRUE),
    n = ~ sum(!is.na(.))
  )))

plf_data_complete_filter %>%
  dplyr::select(contains("bhs")) %>%
  dplyr::summarize(across(everything(), list(
    mean = ~ mean(., na.rm = TRUE),
    sd = ~ sd(., na.rm = TRUE),
    n = ~ sum(!is.na(.))
  )))
```

For equally spaced models, make two datasets from the primary (N = 87) dataset 
  1) excluding month 12 (i.e., months 0-3-6)
  2) excluding month 3 (i.e., months 0-6-12)
  
```{r equal space datasets}
# 3-month interval dataset
plf_data_036 <- plf_data_complete_filter %>%
  filter(month %in% c(0, 3, 6)) 

# 6-month interval dataset
plf_data_0612 <- plf_data_complete_filter %>%
  filter(month %in% c(0, 6, 12))

# Sanity check
plf_data_036 %>% count(month)
plf_data_0612 %>% count(month)
```

# Save data
```{r save data}
# Save dataset
# Sample with both BDI/BHS complete (4 waves), N = 87
write.csv(plf_data_complete_filter,
  file = paste0("01_Output/Created_datasets/Gen_theory_beck_clean_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)

# Sample with BHS & BDI at baseline + one or more follow-ups, N = 157
write.csv(plf_data_bdi_complete_filter_2, 
  file = paste0("01_Output/Created_datasets/Gen_theory_beck_clean_2waves_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)

# Sample with both BDI/BHS complete | 3 month intervals, N = 87
write.csv(plf_data_036, 
  file = paste0("01_Output/Created_datasets/Gen_theory_beck_clean_3mo_interval_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)

# Sample with both BDI/BHS complete | 6 month intervals, N = 87
write.csv(plf_data_0612,
  file = paste0("01_Output/Created_datasets/Gen_theory_beck_clean_6mo_interval_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)
```

# shift data format for main analysis
```{r shift data}
# BHS, N = 87
hope_long_1 <- mlArrange(plf_data_complete_filter,
  grp = "id",
  Time = "month",
  items = c(
    "q01_bhs", "q02_bhs", "q03_bhs", "q04_bhs", "q05_bhs",
    "q06_bhs", "q07_bhs", "q08_bhs", "q09_bhs", "q10_bhs",
    "q11_bhs", "q12_bhs", "q13_bhs", "q14_bhs", "q15_bhs",
    "q16_bhs", "q17_bhs", "q18_bhs", "q19_bhs", "q20_bhs"
  ),
  extra = NULL
)

# BDI-II, N = 87
depr_long_1 <- mlArrange(plf_data_complete_filter,
  grp = "id",
  Time = "month",
  items = c(
    "q01_bdi", "q02_bdi", "q03_bdi", "q04_bdi", "q05_bdi",
    "q06_bdi", "q07_bdi", "q08_bdi", "q09_bdi", "q10_bdi",
    "q11_bdi", "q12_bdi", "q13_bdi", "q14_bdi", "q15_bdi",
    "q16_bdi", "q17_bdi", "q18_bdi", "q19_bdi", "q20_bdi",
    "q21_bdi"
  ),
  extra = NULL
)

# BHS, N = 157
hope_long_2 <- mlArrange(plf_data_bdi_complete_filter_2,
  grp = "id",
  Time = "month",
  items = c(
    "q01_bhs", "q02_bhs", "q03_bhs", "q04_bhs", "q05_bhs",
    "q06_bhs", "q07_bhs", "q08_bhs", "q09_bhs", "q10_bhs",
    "q11_bhs", "q12_bhs", "q13_bhs", "q14_bhs", "q15_bhs",
    "q16_bhs", "q17_bhs", "q18_bhs", "q19_bhs", "q20_bhs"
  ),
  extra = NULL
)

# BDI-II, N = 157
depr_long_2 <- mlArrange(plf_data_bdi_complete_filter_2,
  grp = "id",
  Time = "month",
  items = c(
    "q01_bdi", "q02_bdi", "q03_bdi", "q04_bdi", "q05_bdi",
    "q06_bdi", "q07_bdi", "q08_bdi", "q09_bdi", "q10_bdi",
    "q11_bdi", "q12_bdi", "q13_bdi", "q14_bdi", "q15_bdi",
    "q16_bdi", "q17_bdi", "q18_bdi", "q19_bdi", "q20_bdi",
    "q21_bdi"
  ),
  extra = NULL
)

# BHS, 3 month intervals, N = 87
hope_long_3int <- mlArrange(plf_data_036,
  grp = "id",
  Time = "month",
  items = c(
    "q01_bhs", "q02_bhs", "q03_bhs", "q04_bhs", "q05_bhs",
    "q06_bhs", "q07_bhs", "q08_bhs", "q09_bhs", "q10_bhs",
    "q11_bhs", "q12_bhs", "q13_bhs", "q14_bhs", "q15_bhs",
    "q16_bhs", "q17_bhs", "q18_bhs", "q19_bhs", "q20_bhs"
  ),
  extra = NULL
)

# BHS, 6 month intervals, N = 87
hope_long_6int <- mlArrange(plf_data_0612,
  grp = "id",
  Time = "month",
  items = c(
    "q01_bhs", "q02_bhs", "q03_bhs", "q04_bhs", "q05_bhs",
    "q06_bhs", "q07_bhs", "q08_bhs", "q09_bhs", "q10_bhs",
    "q11_bhs", "q12_bhs", "q13_bhs", "q14_bhs", "q15_bhs",
    "q16_bhs", "q17_bhs", "q18_bhs", "q19_bhs", "q20_bhs"
  ),
  extra = NULL
)

# BDI-II 3 month intervals, N = 87
depr_long_3int <- mlArrange(plf_data_036,
  grp = "id",
  Time = "month",
  items = c(
    "q01_bdi", "q02_bdi", "q03_bdi", "q04_bdi", "q05_bdi",
    "q06_bdi", "q07_bdi", "q08_bdi", "q09_bdi", "q10_bdi",
    "q11_bdi", "q12_bdi", "q13_bdi", "q14_bdi", "q15_bdi",
    "q16_bdi", "q17_bdi", "q18_bdi", "q19_bdi", "q20_bdi",
    "q21_bdi"
  ),
  extra = NULL
)

# BDI-II 6 month intervals, N = 87
depr_long_6int <- mlArrange(plf_data_0612,
  grp = "id",
  Time = "month",
  items = c(
    "q01_bdi", "q02_bdi", "q03_bdi", "q04_bdi", "q05_bdi",
    "q06_bdi", "q07_bdi", "q08_bdi", "q09_bdi", "q10_bdi",
    "q11_bdi", "q12_bdi", "q13_bdi", "q14_bdi", "q15_bdi",
    "q16_bdi", "q17_bdi", "q18_bdi", "q19_bdi", "q20_bdi",
    "q21_bdi"
  ),
  extra = NULL
)


# Save datasets
write.csv(hope_long_1,
  file = paste0("01_Output/Created_datasets/Gen_theory_beck_BHS_long_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)

write.csv(depr_long_1,
  file = paste0("01_Output/Created_datasets/Gen_theory_beck_BDI_long_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)

write.csv(hope_long_2,
  file = paste0("01_Output/Created_datasets/Gen_theory_beck_BHS_long_2waves_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)

write.csv(depr_long_2,
  file = paste0("01_Output/Created_datasets/Gen_theory_beck_BDI_long_2waves_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)

write.csv(hope_long_3int,
  file = paste0("01_Output/Created_datasets/Gen_theory_beck_BHS_long_3int_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)

write.csv(hope_long_6int,
  file = paste0("01_Output/Created_datasets/Gen_theory_beck_BHS_long_6int_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)

write.csv(depr_long_3int,
  file = paste0("01_Output/Created_datasets/Gen_theory_beck_BDI_long_3int_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)

write.csv(depr_long_6int,
  file = paste0("01_Output/Created_datasets/Gen_theory_beck_BDI_long_6int_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)
```


# Baseline BSSI, BHS, & BDI
N = 87
```{r descriptives 87}
# Make baseline dataset
plf_data_baseline <- plf_data_complete_filter[plf_data_complete_filter$month == 0, ]

# BDI-II mean, SD, and range
summary(plf_data_baseline$bdi)
sd(plf_data_baseline$bdi, na.rm = FALSE)
(sum(plf_data_baseline$bdi > 28, na.rm = FALSE) / sum(!is.na(plf_data_baseline$bdi))) * 100

# BHS mean, SD, and range
summary(plf_data_baseline$bhs)
sd(plf_data_baseline$bhs, na.rm = FALSE)
(sum(plf_data_baseline$bhs > 14, na.rm = FALSE) / sum(!is.na(plf_data_baseline$bhs))) * 100
(sum(plf_data_baseline$bhs > 8, na.rm = FALSE) / sum(!is.na(plf_data_baseline$bhs))) * 100

# BSSI
summary(plf_data_baseline$ssi)
sd(plf_data_baseline$ssi, na.rm = TRUE)
sum(plf_data_baseline$ssi > 0, na.rm = TRUE)
(sum(plf_data_baseline$ssi > 0, na.rm = TRUE) / sum(!is.na(plf_data_baseline$ssi))) * 100
```

N = 157
```{r descriptives 157}
# Make baseline dataset
plf_data_baseline_157 <- plf_data_bdi_complete_filter_2[plf_data_bdi_complete_filter_2$month == 0, ]

# BDI-II mean, SD, and range
summary(plf_data_baseline_157$bdi)
sd(plf_data_baseline_157$bdi, na.rm = FALSE)
(sum(plf_data_baseline_157$bdi > 28, na.rm = FALSE) / sum(!is.na(plf_data_baseline_157$bdi))) * 100

# BHS mean, SD, and range
summary(plf_data_baseline_157$bhs)
sd(plf_data_baseline_157$bhs, na.rm = FALSE)
(sum(plf_data_baseline_157$bhs > 14, na.rm = FALSE) / sum(!is.na(plf_data_baseline_157$bhs))) * 100
(sum(plf_data_baseline_157$bhs > 8, na.rm = FALSE) / sum(!is.na(plf_data_baseline_157$bhs))) * 100

# BSSI
nrow(plf_data_baseline_157)
summary(plf_data_baseline_157$ssi)
sum(!is.na(plf_data_baseline_157$ssi))

sd(plf_data_baseline_157$ssi, na.rm = TRUE)
sum(plf_data_baseline_157$ssi > 2, na.rm = TRUE)
(sum(plf_data_baseline_157$ssi > 2, na.rm = TRUE) / sum(!is.na(plf_data_baseline_157$ssi))) * 100
112/160
```

# BHS and BDI descriptives per timepoint 
N = 87
```{r Descriptive timepoints}
# BDI and BHS descriptive statistics split by month
month_descriptives <- psych::describeBy(plf_data_complete_filter[, c("bhs", "bdi")],
  plf_data_complete_filter$month,
  IQR = TRUE
)

month_0 <- month_descriptives$"0"
month_3 <- month_descriptives$"3"
month_6 <- month_descriptives$"6"
month_12 <- month_descriptives$"12"

all_months <- rbind(month_0, month_3, month_6, month_12)

# Save table
write.csv(all_months,
  file = paste0("01_Output/Results/descriptives_table_", format(Sys.Date(), "%Y_%m_%d"), ".csv"),
  row.names = TRUE
)
```

# BDI baseline PCA 
```{r bdi pca 87}
plf_data_m0 <- plf_data_complete_filter %>%
  filter(month == 0)

bdi_items <- plf_data_m0 %>%
  dplyr::select(ends_with("_bdi")) %>%
  na.omit()

# KMO & bartlett
bdi_kmo <- EFAtools::KMO(bdi_items)
bdi_bartlett <- EFAtools::BARTLETT(bdi_items)

bdi_kmo
bdi_bartlett

# BDI - standard PCA (ordinal items)
bdi_pca <- prcomp(bdi_items, 
                  scale. = TRUE)

summary(bdi_pca)

# Scree plot for BDI-II
plot(bdi_pca, type = "l", main = "Scree plot for bdi")

# Summary of explained variance
summary(bdi_pca)
```

```{r bdi pca 157}
plf_data_m0_2 <- plf_data_bhs_complete_filter_2 %>%
  filter(month == 0)

bdi_items <- plf_data_m0_2 %>%
  dplyr::select(ends_with("_bdi")) %>%
  na.omit()

# KMO & bartlett
bdi_kmo <- EFAtools::KMO(bdi_items)
bdi_bartlett <- EFAtools::BARTLETT(bdi_items)

bdi_kmo
bdi_bartlett

# BDI - standard PCA (ordinal items)
bdi_pca <- prcomp(bdi_items, 
                  scale. = TRUE)

# Summary of explained variance
summary(bdi_pca)
```

# BHS baseline PCA 
```{r bhs pca 87}
bhs_items_1 <- plf_data_m0 %>%
  dplyr::select(ends_with("_bhs")) %>%
  na.omit()

bhs_tetra_1 <- tetrachoric(bhs_items_1)$rho

fa.parallel(bhs_tetra_1,
            fa = "pc",
            n.iter = 100,
            n.obs = nrow(bhs_items_1),
            main = "Parallel Analysis: BHS")

bhs_pca_1 <- principal(bhs_tetra_1, nfactors = ncol(bhs_items_1), rotate = "none")
bhs_pca_1
```

```{r bhs pca 157}
bhs_items_2 <- plf_data_m0_2 %>%
  dplyr::select(ends_with("_bhs")) %>%
  na.omit()

bhs_tetra_2 <- tetrachoric(bhs_items_2)$rho

fa.parallel(bhs_tetra_2,
            fa = "pc",
            n.iter = 100,
            n.obs = nrow(bhs_items_2),
            main = "Parallel Analysis: BHS")

bhs_pca_2 <- principal(bhs_tetra_2, nfactors = ncol(bhs_items_2), rotate = "none")
bhs_pca_2
```

# BHS and BDI reliability alpha per timepoint
```{r cr timepoints}
# BDI
bdi <- plf_data_complete_filter %>%
  select(month, matches("^q\\d{2}_bdi$"))

bdi_items_timepoint_0 <- bdi %>%
  filter(month == 0) %>%
  select(-month)

bdi_items_timepoint_3 <- bdi %>%
  filter(month == 3) %>%
  select(-month)

bdi_items_timepoint_6 <- bdi %>%
  filter(month == 6) %>%
  select(-month)

bdi_items_timepoint_12 <- bdi %>%
  filter(month == 12) %>%
  select(-month)

ltm::cronbach.alpha(bdi_items_timepoint_0, CI = TRUE, na.rm = TRUE)  
ltm::cronbach.alpha(bdi_items_timepoint_3, CI = TRUE, na.rm = TRUE)  
ltm::cronbach.alpha(bdi_items_timepoint_6, CI = TRUE, na.rm = TRUE)  
ltm::cronbach.alpha(bdi_items_timepoint_12, CI = TRUE, na.rm = TRUE) 

# BHS
bhs <- plf_data_complete_filter %>%
  select(month, matches("^q\\d{2}_bhs$"))

bhs_items_timepoint_0 <- bhs %>%
  filter(month == 0) %>%
  select(-month)

bhs_items_timepoint_3 <- bhs %>%
  filter(month == 3) %>%
  select(-month)

bhs_items_timepoint_6 <- bhs %>%
  filter(month == 6) %>%
  select(-month)

bhs_items_timepoint_12 <- bhs %>%
  filter(month == 12) %>%
  select(-month)

ltm::cronbach.alpha(bhs_items_timepoint_0, CI = TRUE, na.rm = TRUE)  
ltm::cronbach.alpha(bhs_items_timepoint_3, CI = TRUE, na.rm = TRUE)  
ltm::cronbach.alpha(bhs_items_timepoint_6, CI = TRUE, na.rm = TRUE)  
ltm::cronbach.alpha(bhs_items_timepoint_12, CI = TRUE, na.rm = TRUE) 
```

# BHS endorsement (means/variance), primary sample
```{r bhs endorsement}
plf_data_m0 <- plf_data_complete_filter[plf_data_complete_filter$month == 0, ]
plf_data_m3 <- plf_data_complete_filter[plf_data_complete_filter$month == 3, ]
plf_data_m6 <- plf_data_complete_filter[plf_data_complete_filter$month == 6, ]
plf_data_m12 <- plf_data_complete_filter[plf_data_complete_filter$month == 12, ]

bhs_items_m0 <- plf_data_m0 %>% select(ends_with("_bhs"))  
item_means_m0 <- colMeans(bhs_items_m0, na.rm = TRUE)
item_vars_m0 <- item_means_m0 * (1 - item_means_m0)

bhs_items_m3 <- plf_data_m3 %>% select(ends_with("_bhs"))  
item_means_m3 <- colMeans(bhs_items_m3, na.rm = TRUE)
item_vars_m3 <- item_means_m3 * (1 - item_means_m3)

bhs_items_m6 <- plf_data_m6 %>% select(ends_with("_bhs"))  
item_means_m6 <- colMeans(bhs_items_m6, na.rm = TRUE)
item_vars_m6 <- item_means_m6 * (1 - item_means_m6)

bhs_items_m12 <- plf_data_m12 %>% select(ends_with("_bhs"))  
item_means_m12 <- colMeans(bhs_items_m12, na.rm = TRUE)
item_vars_m12 <- item_means_m12 * (1 - item_means_m12)
 
summary(item_means_m0)
summary(item_vars_m0)

summary(item_means_m3)
summary(item_vars_m3)

summary(item_means_m6)
summary(item_vars_m6)

summary(item_means_m12)
summary(item_vars_m12)
```

# Demographics 87
```{r demographics 87}
sex_demo_table <- table(plf_data_complete_filter$sex_demo)
sex_demo_percent <- (sex_demo_table / 87) * 100

latino_demo_table <- table(plf_data_complete_filter$latino_demo)
latino_demo_percent <- (latino_demo_table / 87) * 100

race_demo_table <- table(plf_data_complete_filter$race_demo)
race_demo_percent <- (race_demo_table / 87) * 100

degree_demo_table <- table(plf_data_complete_filter$degree_demo)
degree_demo_percent <- (degree_demo_table / 87) * 100

employ_demo_table <- table(plf_data_complete_filter$employ_demo)
employ_demo_percent <- (employ_demo_table / 87) * 100

marry_demo_table <- table(plf_data_complete_filter$marry_demo)
marry_demo_percent <- (marry_demo_table / 87) * 100

treat_demo_table <- table(plf_data_complete_filter$treat_demo)
treat_demo_percent <- (treat_demo_table / 87) * 100

prior_demo_table <- table(plf_data_complete_filter$prior_demo)
prior_demo_percent <- (prior_demo_table / 87) * 100

prison_demo_table <- table(plf_data_complete_filter$prison_demo)
prison_demo_percent <- (prison_demo_table / 87) * 100

summary(plf_data_complete_filter[plf_data_complete_filter$month == 0, ]$age_demo)
sd(plf_data_complete_filter[plf_data_complete_filter$month == 0, ]$age_demo, na.rm = TRUE)

table(plf_data_complete_filter$bpd)
table(plf_data_complete_filter$msibpd)
```

```{r demographics 157}
sex_demo_table <- table(plf_data_baseline_157$sex_demo)
sex_demo_percent <- (sex_demo_table / 157) * 100

latino_demo_table <- table(plf_data_baseline_157$latino_demo)
latino_demo_percent <- (latino_demo_table / 157) * 100

race_demo_table <- table(plf_data_baseline_157$race_demo)
race_demo_percent <- (race_demo_table / 157) * 100

degree_demo_table <- table(plf_data_baseline_157$degree_demo)
degree_demo_percent <- (degree_demo_table / 157) * 100

employ_demo_table <- table(plf_data_baseline_157$employ_demo)
employ_demo_percent <- (employ_demo_table / 157) * 100

marry_demo_table <- table(plf_data_baseline_157$marry_demo)
marry_demo_percent <- (marry_demo_table / 157) * 100

treat_demo_table <- table(plf_data_baseline_157$treat_demo)
treat_demo_percent <- (treat_demo_table / 157) * 100

prior_demo_table <- table(plf_data_baseline_157$prior_demo)
prior_demo_percent <- (prior_demo_table / 157) * 100

prison_demo_table <- table(plf_data_baseline_157$prison_demo)
prison_demo_percent <- (prison_demo_table / 157) * 100

prison_demo_table
prison_demo_percent

summary(plf_data_baseline_157[plf_data_baseline_157$month == 0, ]$age_demo)
sd(plf_data_baseline_157[plf_data_baseline_157$month == 0, ]$age_demo, na.rm = TRUE)
```

# MINI MDD info
```{r mini 87}
# mini01 = major depressive episode
## when01c = current
## when01p = past
## when01r = recurrent

colnames(plf_data_complete_filter)

table(plf_data_complete_filter$mini01_mini) # 0 = 2, 1 = 81 (83 total)
table(plf_data_complete_filter$when01c_mini) # 0 = 9, 1 = 68 (77 total)
68/87
table(plf_data_complete_filter$when01p_mini) # 0 = 26, 1 = 51 (77 total)
51/87
table(plf_data_complete_filter$when01r_mini) # 0 = 22, 1 = 55 (77 total)
55/87

# Does everyone have a past, current, *or* recurrent MDE?
has_one <- (plf_data_complete_filter$when01c_mini == 1) |
  (plf_data_complete_filter$when01p_mini == 1) |
  (plf_data_complete_filter$when01r_mini == 1)

sum(has_one, na.rm = TRUE)
77/87
```

MINI 157
```{r}
# mini01 = major depressive episode
## when01c = current
## when01p = past
## when01r = recurrent

nrow(plf_data_baseline_157)
table(plf_data_baseline_157$when01c_mini) # 0 = 18, 1 = 119 (=137)
119/157
table(plf_data_baseline_157$when01p_mini) # 0 = 44, 1 = 93 (=137)
93/157
table(plf_data_baseline_157$when01r_mini) # 0 = 37, 1 = 100 (=137)
100/157

# Does everyone have a past, current, *or* recurrent MDE?
has_one <- (plf_data_baseline_157$when01c_mini == 1) |
  (plf_data_baseline_157$when01p_mini == 1) |
  (plf_data_baseline_157$when01r_mini == 1)

sum(has_one, na.rm = TRUE)
137/157
```


